The Impact of Malaria Episodes and Treatment Regimens on Adverse Pregnancy Outcomes in Ugandan Women

### 2025-03-30 products/manuscript/Manuscript.qmd
malo

promo_data_clean <- read.csv(here("data", "clean", "PROMO_Data_clean.csv"))

@@

```{r, echo=FALSE, eval=knitr::is_html_output(), message=FALSE, warning=FALSE}
library(flextable)
table_data %>%
  flextable() %>%
  autofit()

# Create table_data as before:
table_data <- tribble(
  ~Characteristic, ~Subcategory, ~`Monthly SP (n=391)`, ~`Monthly DP (n=391)`,
  "Age, years", "", "23 (19–27)", "23 (19–27)",
  "Gestational Age at Enrollment (weeks)", "", "15.4 (13.3–17.6)", "15.0 (13.4–17.1)",
  "", "12–16", "66 (17%)", "62 (15.8%)",
  "", "17–20", "164 (42.2%)", "197 (50.1%)",
  "", "21–24", "133 (34.2%)", "118 (30%)",
  "Gravidity", "", "1.2 (0.9–1.7)", "1.1 (0.8–1.6)",
  "", "1", "102 (26%)", "95 (24%)",
  "", "2–3", "180 (46%)", "190 (49%)",
  "", "≥4", "109 (28%)", "106 (27%)",
  "Parity", "", "2.43 (1.67)", "2.43 (1.65)",
  "", "0", "140 (36%)", "145 (37%)",
  "", "1–2", "170 (44%)", "165 (42%)",
  "", "≥3", "81 (20%)", "81 (21%)",
  "Total Malaria Episodes (mean (SD))", "", "1.06 (1.03)", "0.98 (0.95)",
  "Maternal Nutritional Status/BMI (mean (SD))", "", "22.5 (3.2)", "22.8 (3.1)",
  "History of Previous Malaria Episodes (%)", "", "40 (10%)", "35 (9%)",
  "Maternal Education Level (%)", "", "", "",
  "", "A and O Level", "194 (49.4%)", "187 (48.1%)",
  "", "Primary", "68 (17.3%)", "71 (18.3%)",
  "", "Tertiary", "65 (16.5%)", "61 (15.7%)",
  "", "University", "66 (16.8%)", "70 (18.0%)"
)

# Render the table with pandoc format:
kable(table_data, format = "pandoc", caption = "Table 1. Baseline Characteristics")

>>>>

promo_data_clean <- read.csv(here("data", "clean", "PROMO_Data_clean.csv"))
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}

# Create table data
table_data <- tribble(
  ~Characteristic, ~Subcategory, ~`Monthly SP (n=391)`, ~`Monthly DP (n=391)`,
  "Age, years", "", "23 (19–27)", "23 (19–27)",
  "Gestational Age at Enrollment (weeks)", "", "15.4 (13.3–17.6)", "15.0 (13.4–17.1)",
  "", "12–16", "66 (17%)", "62 (15.8%)",
  "", "17–20", "164 (42.2%)", "197 (50.1%)",
  "", "21–24", "133 (34.2%)", "118 (30%)",
  "Gravidity", "", "1.2 (0.9–1.7)", "1.1 (0.8–1.6)",
  "", "1", "102 (26%)", "95 (24%)",
  "", "2–3", "180 (46%)", "190 (49%)",
  "", "≥4", "109 (28%)", "106 (27%)",
  "Parity", "", "2.43 (1.67)", "2.43 (1.65)",
  "", "0", "140 (36%)", "145 (37%)",
  "", "1–2", "170 (44%)", "165 (42%)",
  "", "≥3", "81 (20%)", "81 (21%)",
  "Total Malaria Episodes (mean (SD))", "", "1.06 (1.03)", "0.98 (0.95)",
  "Maternal Nutritional Status/BMI (mean (SD))", "", "22.5 (3.2)", "22.8 (3.1)",
  "History of Previous Malaria Episodes (%)", "", "40 (10%)", "35 (9%)",
  "Maternal Education Level (%)", "", "", "",
  "", "A and O Level", "194 (49.4%)", "187 (48.1%)",
  "", "Primary", "68 (17.3%)", "71 (18.3%)",
  "", "Tertiary", "65 (16.5%)", "61 (15.7%)",
  "", "University", "66 (16.8%)", "70 (18.0%)"
)

# Render the table in DOCX-compatible format
kable(
  table_data,
  format = "pandoc",
  caption =
)
